Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-15 paper/main.tex
working on discussion, added some text and notes

% connections to prior work: context effects, priming, situation models

% implications for adaptive learning, education and training

>>>>

We asked participants to study and freely recall word lists. The words on each
list (and the set of lists) were held constant across participants. For each
word, we considered (and manipulated) two semantic features (category and size)
that reflected aspects of the \textit{meanings} of the words, along with two
lexicographic features (word length and first letter), which reflected aspects
of the words' \textit{letters}. These semantic and lexicographic features are
intrinsic to each word. We also considered and manipulated two additional
visual features (color and location) that affected the \textit{appearance} of
each studied item, but could be varied independently of the words' identities.
Across different experimental conditions, we manipulated how the visual
features varied across words (within each list), along with the orders of each
list's words. Although participants' task (verbally recalling as many words as
possible, in any order, within one minute) remained constant across all of
these conditions, and although the set of words they studied on each list
remained constant, our manipulations substantially affected participants'
memories. The impact of some of the manipulations also affected how
participants remembered \textit{future} lists that were sorted randomly.

% specific findings:
%   reduced (early/late) vs. feature rich and reduced: event boundaries
%   order manipulations: lingering effects
%   adaptive condition: people have unique preferences, and matching them can improve their memory and affect how the remembered info is organized

% connections to prior work: 
%     - context effects: 
%     - priming: 
%     - situation models:

% implications for:
%     - theory: flexibility in how we organize information, bridge between "classic" and naturalistic experiments
%     - applications: adaptive learning, education and training

% concluding remarks:
%    - what are the limits of human learning?  how much does what we remember depend on how we experience it?  our expectations, strategies, situation models, etc. shape how our experiences are remembered.
%    - but those aspects of our memory are not fixed: when we are exposed to the same experience in a new way, it can change how we remember it and how we
%      remember *future* experiences
